---
title: "Lego E4-7 & Combined In-Lab/Online Analyses"
author: Mona Zhu
date: Updated February 7, 2020
output: 
  html_document:
    fig_width: 8
    fig_height: 5
    toc: true
    toc_float: true
    theme: cerulean
    highlight: tango
    code_folding: hide
---

<style>
pre code, pre, code {
  overflow-y: auto !important;
  max-height: 20em;
}
</style>

```{r, message=F, warning=F}
# libraries
library(car)
library(ggplot2)
library(reshape2)
library(sjPlot)
library(corrgram)
library(apaTables)
# library(irr)
```

```{r }
# setwd("C:/Users/monaj/Dropbox/CANB Lab/Lego & Search/Online Lego Study")
df<-read.csv("C:/Users/MonaZhu/Dropbox/CANB Lab/Lego & Search/Combined Data/Lego_Combined In-Lab&Turk&SONA_9Dec2019.csv")

df$StudyType<-factor(ifelse(df$Study=="Sona E1"|df$Study=="Sona E2", "Sona", 
                     ifelse(df$Study=="Mturk E1"|df$Study=="Mturk E2"|df$Study=="Mturk E3", "Mturk", "In Lab")))

# Pre-Task Choice
df$Choice<-factor(recode(as.character(df$Choice), "''=NA; 'Categorize then search'='Organization'; 
                  'Search without categorizing'='Search Only'"))
df$Choice<-factor(df$Choice, levels(df$Choice)[c(2,1)])
df$Choice.Num<-ifelse(df$Choice=="Organization", 1, 0)

# Post-Task Choice (in-lab only)
df$Future.Choice<-factor(recode(as.character(df$Future.Choice), "''=NA; 
                                'Categorize then search'='Organization'; 
                                'Search without categorizing'='Search Only'"))
df$Future.Choice<-factor(df$Future.Choice, levels(df$Future.Choice)[c(2,1)])
df$FutureChoice.Num<-ifelse(df$Future.Choice=="Organization", 1, 0)

# Assigned Condition (in-lab only)
df$Condition<-factor(recode(as.character(df$Condition), "''=NA; 'Categorize then search'='Organization';
                     'Search without categorizing'='Search Only'"))
df$Condition<-factor(df$Condition, levels(df$Condition)[c(2,1)])

# Recoding other variables
df$PreTimeDiff<-as.numeric(df$Time_SearchTotal-df$Time_OrgTotal)
df$PostTimeDiff<-as.numeric(df$PostTime_SearchTotal-df$PostTime_OrgTotal)
df$PreEffDiff<-as.numeric(df$Search.Eff-df$Org.Eff)
df$PostEffDiff<-as.numeric(df$PostSearch.Eff-df$PostOrg.Eff)
df$FunDiff<-as.numeric(df$Search.Fun-df$Org.Fun)
df$Switch<-ifelse(is.na(df$Future.Choice), NA, 
                  ifelse(df$Choice==df$Future.Choice, "Same", "Switched"))
df$Switch.Num<-ifelse(df$Switch=="Same", 0, 1)

# time<-df[complete.cases(df$Time_Org.min), ] # data set where time estimation was measured
# eff<-df[complete.cases(df$Org.Eff), ] # dataset
# fun<-df[complete.cases(df$Org.Fun), ]
# post<-df[!is.na(df$Future.Choice),]
```

# mturk: MTurk
```{r}
mturk.raw<-subset(df, Study %in% c("Mturk E2", "Mturk E3"))
mturk<-subset(mturk.raw, !is.na(Age))
mturk$Study<-as.factor(as.character(mturk$Study))
```


### Demographics

Sex:

```{r}
table(mturk$Sex)
table(mturk$Sex, mturk$Study)

```

Mean age and SD respectively: 
```{r}
mean(mturk$Age)
sd(mturk$Age)

```

Sample 1:
```{r}
mean(mturk[mturk$Study=="Mturk E2",]$Age)
sd(mturk[mturk$Study=="Mturk E2",]$Age)

```

Sample 2:
```{r}
mean(mturk[mturk$Study=="Mturk E3",]$Age)
sd(mturk[mturk$Study=="Mturk E3",]$Age)

```











### Raw Estimates

#### Time


Graph:

```{r}
time.mturk<-melt(mturk, id=c(1:9, 11:12, 14:ncol(mturk)),
                 variable.name = "Strategy", value.name = "Time") # col 10 & 13 are the time estimates
time.mturk$Strategy<-factor(recode(time.mturk$Strategy, "'Time_OrgTotal'='Organization';
                                   'Time_SearchTotal'='Search Only'"))

ggplot(time.mturk, aes(x = Strategy, y = Time))+
  facet_grid(.~Study)+
  geom_violin()+
  geom_boxplot(width=0.1)

```

Wilcoxon Ranked Sign Test: 
```{r}
wilcox.test(mturk$Time_OrgTotal, mturk$Time_SearchTotal, paired=T) 
```


Sample 1: 
```{r}
wilcox.test(mturk[mturk$Study=="Mturk E2",]$Time_OrgTotal, mturk[mturk$Study=="Mturk E2",]$Time_SearchTotal, paired=T, exact=F) 
```

Sample 2: 
```{r}
wilcox.test(mturk[mturk$Study=="Mturk E3",]$Time_OrgTotal, mturk[mturk$Study=="Mturk E3",]$Time_SearchTotal, paired=T, exact=F) 
```







Estimated median time for the organization strategy:
```{r}
median(mturk$Time_OrgTotal)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(mturk[mturk$Study=="Mturk E2",]$Time_OrgTotal)
median(mturk[mturk$Study=="Mturk E3",]$Time_OrgTotal)
```

Estimated median time for the search-only strategy:
```{r}
median(mturk$Time_SearchTotal)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(mturk[mturk$Study=="Mturk E2",]$Time_SearchTotal)
median(mturk[mturk$Study=="Mturk E3",]$Time_SearchTotal)
```
Estimated mean time and sd that participants expect to spend in the organization phase, if they were to use the organization strategy:

Table breaking down the number of individuals who thought the search-only strategy was slower, faster, or the same as the organization strategy: 

```{r}
mturk$time.compare<-ifelse(mturk$Time_OrgTotal>mturk$Time_SearchTotal, "Search Faster", 
                     ifelse(mturk$Time_OrgTotal<mturk$Time_SearchTotal, "Organize Faster", "Same"))
table(mturk$time.compare)

```


#### Effort


Graph:

```{r}
eff.mturk<-melt(mturk, id=c(1:13, 16:ncol(mturk)),
                 variable.name = "Strategy", value.name = "Effort") # col 10 & 13 are the time estimates
eff.mturk$Strategy<-factor(recode(eff.mturk$Strategy, "'Org.Eff'='Organization';
                                   'Search.Eff'='Search Only'"))

ggplot(eff.mturk, aes(x = Strategy, y = Effort))+
  facet_grid(.~Study)+
  geom_violin()+
  geom_boxplot(width=0.1)

```

Wilcoxon Ranked Sign Test: 
```{r}
wilcox.test(mturk$Org.Eff, mturk$Search.Eff, paired=T) 
```


Sample 1: 
```{r}
wilcox.test(mturk[mturk$Study=="Mturk E2",]$Org.Eff, mturk[mturk$Study=="Mturk E2",]$Search.Eff, paired=T, exact=F) 
```

Sample 2: 
```{r}
wilcox.test(mturk[mturk$Study=="Mturk E3",]$Org.Eff, mturk[mturk$Study=="Mturk E3",]$Search.Eff, paired=T, exact=F) 
```







Estimated median time for the organization strategy:
```{r}
median(mturk$Org.Eff)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(mturk[mturk$Study=="Mturk E2",]$Org.Eff)
median(mturk[mturk$Study=="Mturk E3",]$Org.Eff)
```

Estimated median time for the search-only strategy:
```{r}
median(mturk$Search.Eff)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(mturk[mturk$Study=="Mturk E2",]$Search.Eff)
median(mturk[mturk$Study=="Mturk E3",]$Search.Eff)
```
Estimated mean time and sd that participants expect to spend in the organization phase, if they were to use the organization strategy:

Table breaking down the number of individuals who thought the search-only strategy was slower, faster, or the same as the organization strategy: 

```{r}
mturk$time.compare<-ifelse(mturk$Org.Eff>mturk$Search.Eff, "Search Faster", 
                     ifelse(mturk$Org.Eff<mturk$Search.Eff, "Organize Faster", "Same"))
table(mturk$time.compare)

```






#### Enjoyability


Graph:

```{r}
fun.mturk<-melt(mturk, id=c(1:15, 18:ncol(mturk)),
                 variable.name = "Strategy", value.name = "Enjoyability") # col 10 & 13 are the time estimates
fun.mturk$Strategy<-factor(recode(fun.mturk$Strategy, "'Org.Fun'='Organization';
                                   'Search.Fun'='Search Only'"))

ggplot(fun.mturk, aes(x = Strategy, y = Enjoyability))+
  facet_grid(.~Study)+
  geom_violin()+
  geom_boxplot(width=0.1)

```

Wilcoxon Ranked Sign Test: 
```{r}
wilcox.test(mturk$Org.Fun, mturk$Search.Fun, paired=T) 
```


Sample 1: 
```{r}
wilcox.test(mturk[mturk$Study=="Mturk E2",]$Org.Fun, mturk[mturk$Study=="Mturk E2",]$Search.Fun, paired=T, exact=F) 
```

Sample 2: 
```{r}
wilcox.test(mturk[mturk$Study=="Mturk E3",]$Org.Fun, mturk[mturk$Study=="Mturk E3",]$Search.Fun, paired=T, exact=F) 
```







Estimated median time for the organization strategy:
```{r}
median(mturk$Org.Fun)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(mturk[mturk$Study=="Mturk E2",]$Org.Fun)
median(mturk[mturk$Study=="Mturk E3",]$Org.Fun)
```

Estimated median time for the search-only strategy:
```{r}
median(mturk$Search.Fun)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(mturk[mturk$Study=="Mturk E2",]$Search.Fun)
median(mturk[mturk$Study=="Mturk E3",]$Search.Fun)
```
Estimated mean time and sd that participants expect to spend in the organization phase, if they were to use the organization strategy:

Table breaking down the number of individuals who thought the search-only strategy was slower, faster, or the same as the organization strategy: 

```{r}
mturk$time.compare<-ifelse(mturk$Org.Fun>mturk$Search.Fun, "Organization More Enjoyable", 
                     ifelse(mturk$Org.Fun<mturk$Search.Fun, "Search More Enjoyable", "Same"))
table(mturk$time.compare)

```






### Strategy preference

#### Overall Preference

(With sample as factor)
```{r}
chisq.test(table(mturk$Choice, mturk$Study))
table(mturk$Choice, mturk$Study)
```

```{r}
chisq.test(table(mturk$Choice))
# table(mturk$Choice)
60/(60+20) # number of individuals choosing organization
```



#### Time, Effort, & Enjoyability Estimates Predicting Choice


Models with single predictor 
```{r}
mturk.time<-glm(Choice.Num ~ PreTimeDiff, family="binomial", data=mturk)
# quasi-separation with mturk.time model
mturk.time1<-glm(Choice.Num ~ PreTimeDiff, family="binomial", data=mturk[mturk$PreTimeDiff<70,])
mturk.eff<-glm(Choice.Num ~ PreEffDiff, family="binomial", data=mturk[mturk$PreTimeDiff<70,])
mturk.fun<-glm(Choice.Num ~ FunDiff, family="binomial", data=mturk[mturk$PreTimeDiff<70,])

tab_model(mturk.time1, mturk.eff, mturk.fun, transform=NULL, show.stat = T, digits.p=2)
```


The same models as above except looking at whether they interact with sample

```{r}
mturk.time2<-glm(Choice.Num ~ PreTimeDiff*Study, family="binomial", data=mturk[mturk$PreTimeDiff<70,])
mturk.eff2<-glm(Choice.Num ~ PreEffDiff*Study, family="binomial", data=mturk[mturk$PreTimeDiff<70,])
mturk.fun2<-glm(Choice.Num ~ FunDiff*Study, family="binomial", data=mturk[mturk$PreTimeDiff<70,])

tab_model(mturk.time2, mturk.eff2, mturk.fun2, transform=NULL, show.stat = T, digits.p=2)
```



#### Correlation between estimated task time, effort, & enjoyability

```{r}
corrgram(mturk[c("PreTimeDiff", "PreEffDiff", "FunDiff")],
         lower.panel=panel.pts, upper.panel=panel.conf,
         diag.panel=panel.density)

```

```{r}
iv<-mturk[c("PreTimeDiff", "PreEffDiff", "FunDiff")]
names(iv)<-c("Relative Task Time", "Relative Task Effort", "Relative Task Enjoyability")

apa.cor.table(iv, table.number = 1, filename = "LegoOnline_Table1.doc")

```


Model with all factors combined
```{r, warning=F, message=F}
mturk.all<-glm(Choice.Num ~ PreTimeDiff+PreEffDiff+FunDiff, family="binomial", data=mturk[mturk$PreTimeDiff<70,])
mturk.all2<-glm(Choice.Num ~ PreTimeDiff*Study+PreEffDiff*Study+FunDiff*Study, family="binomial", data=mturk[mturk$PreTimeDiff<70,])

tab_model(mturk.all, transform=NULL, show.stat = T, digits.p=2)
```


```{r}
ggplot(mturk, aes(x=PreTimeDiff, y=Choice.Num)) + 
  geom_point(position = "jitter") + 
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)

# par(mar = c(4, 4, 1, 1)) # Reduce some of the margins so that the plot fits better
# plot(dat$mpg, dat$vs)
# curve(predict(logr_vm, data.frame(mpg=x), type="response"), add=TRUE) 
```

```{r}
plot_model(mturk.pre3, type="int")
```
































# SONA
```{r}
sona.raw<-subset(df, Study %in% c("Sona E1", "Sona E2"))
sona<-subset(sona.raw, !is.na(Age))
sona$Study<-as.factor(as.character(sona$Study))
```


### Demographics

Sex:

```{r}
table(sona$Sex)
table(sona$Sex, sona$Study)

```

Mean age and SD respectively: 
```{r}
mean(sona$Age)
sd(sona$Age)

```

Sample 1:
```{r}
mean(sona[sona$Study=="Sona E1",]$Age)
sd(sona[sona$Study=="Sona E1",]$Age)

```

Sample 2:
```{r}
mean(sona[sona$Study=="Sona E2",]$Age)
sd(sona[sona$Study=="Sona E2",]$Age)

```




### Raw Estimates

#### Task Time

Graph:

```{r}
sona<-sona[complete.cases(sona$PreTimeDiff),] # removing data from individuals without numerical data for time estimates

time.sona<-melt(sona, id=c(1:9, 11:12, 14:ncol(sona)),
                 variable.name = "Strategy", value.name = "Time") # col 10 & 13 are the time estimates
time.sona$Strategy<-factor(recode(time.sona$Strategy, "'Time_OrgTotal'='Organization';
                                   'Time_SearchTotal'='Search Only'"))

ggplot(time.sona, aes(x = Strategy, y = Time))+
  facet_grid(.~Study)+
  geom_violin()+
  geom_boxplot(width=0.1)

```

Wilcoxon Ranked Sign Test: 
```{r}
wilcox.test(sona$Time_OrgTotal, sona$Time_SearchTotal, paired=T) 
```


Sample 1: 
```{r}
wilcox.test(sona[sona$Study=="Sona E1",]$Time_OrgTotal, sona[sona$Study=="Sona E1",]$Time_SearchTotal, paired=T, exact=F) 
```

Sample 2: 
```{r}
wilcox.test(sona[sona$Study=="Sona E2",]$Time_OrgTotal, sona[sona$Study=="Sona E2",]$Time_SearchTotal, paired=T, exact=F) 
```







Estimated median time for the organization strategy:
```{r}
median(sona$Time_OrgTotal)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(sona[sona$Study=="Sona E1",]$Time_OrgTotal)
median(sona[sona$Study=="Sona E2",]$Time_OrgTotal)
```

Estimated median time for the search-only strategy:
```{r}
median(sona$Time_SearchTotal)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(sona[sona$Study=="Sona E1",]$Time_SearchTotal)
median(sona[sona$Study=="Sona E2",]$Time_SearchTotal)
```




```{r}
sona$time.compare<-ifelse(sona$Time_OrgTotal>sona$Time_SearchTotal, "Search Faster", 
                     ifelse(sona$Time_OrgTotal<sona$Time_SearchTotal, "Organize Faster", "Same"))
table(sona$time.compare)

```



#### Effort


Graph:

```{r}
eff.sona<-melt(sona, id=c(1:13, 16:ncol(sona)),
                 variable.name = "Strategy", value.name = "Effort") # col 10 & 13 are the time estimates
eff.sona$Strategy<-factor(recode(eff.sona$Strategy, "'Org.Eff'='Organization';
                                   'Search.Eff'='Search Only'"))

ggplot(eff.sona, aes(x = Strategy, y = Effort))+
  facet_grid(.~Study)+
  geom_violin()+
  geom_boxplot(width=0.1)

```

Wilcoxon Ranked Sign Test: 
```{r}
wilcox.test(sona$Org.Eff, sona$Search.Eff, paired=T) 
```


Sample 1: 
```{r}
wilcox.test(sona[sona$Study=="Sona E1",]$Org.Eff, sona[sona$Study=="Sona E1",]$Search.Eff, paired=T, exact=F) 
```

Sample 2: 
```{r}
wilcox.test(sona[sona$Study=="Sona E2",]$Org.Eff, sona[sona$Study=="Sona E2",]$Search.Eff, paired=T, exact=F) 
```







Estimated median time for the organization strategy:
```{r}
median(sona$Org.Eff)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(sona[sona$Study=="Sona E1",]$Org.Eff)
median(sona[sona$Study=="Sona E2",]$Org.Eff)
```

Estimated median time for the search-only strategy:
```{r}
median(sona$Search.Eff)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(sona[sona$Study=="Sona E1",]$Search.Eff)
median(sona[sona$Study=="Sona E2",]$Search.Eff)
```
Estimated mean time and sd that participants expect to spend in the organization phase, if they were to use the organization strategy:

Table breaking down the number of individuals who thought the search-only strategy was slower, faster, or the same as the organization strategy: 

```{r}
sona$time.compare<-ifelse(sona$Org.Eff>sona$Search.Eff, "Search Faster", 
                     ifelse(sona$Org.Eff<sona$Search.Eff, "Organize Faster", "Same"))
table(sona$time.compare)

```






#### Enjoyability


Graph:

```{r}
fun.sona<-melt(sona, id=c(1:15, 18:ncol(sona)),
                 variable.name = "Strategy", value.name = "Enjoyability") # col 10 & 13 are the time estimates
fun.sona$Strategy<-factor(recode(fun.sona$Strategy, "'Org.Fun'='Organization';
                                   'Search.Fun'='Search Only'"))

ggplot(fun.sona, aes(x = Strategy, y = Enjoyability))+
  facet_grid(.~Study)+
  geom_violin()+
  geom_boxplot(width=0.1)

```

Wilcoxon Ranked Sign Test: 
```{r}
wilcox.test(sona$Org.Fun, sona$Search.Fun, paired=T) 
```


Sample 1: 
```{r}
wilcox.test(sona[sona$Study=="Sona E1",]$Org.Fun, sona[sona$Study=="Sona E1",]$Search.Fun, paired=T, exact=F) 
```

Sample 2: 
```{r}
wilcox.test(sona[sona$Study=="Sona E2",]$Org.Fun, sona[sona$Study=="Sona E2",]$Search.Fun, paired=T, exact=F) 
```







Estimated median time for the organization strategy:
```{r}
median(sona$Org.Fun)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(sona[sona$Study=="Sona E1",]$Org.Fun)
median(sona[sona$Study=="Sona E2",]$Org.Fun)
```

Estimated median time for the search-only strategy:
```{r}
median(sona$Search.Fun)
```

Medians for Sample 1 and 2 respectively:
```{r}
median(sona[sona$Study=="Sona E1",]$Search.Fun)
median(sona[sona$Study=="Sona E2",]$Search.Fun)
```
Estimated mean time and sd that participants expect to spend in the organization phase, if they were to use the organization strategy:

Table breaking down the number of individuals who thought the search-only strategy was slower, faster, or the same as the organization strategy: 

```{r}
sona$time.compare<-ifelse(sona$Org.Fun>sona$Search.Fun, "Organization More Enjoyable", 
                     ifelse(sona$Org.Fun<sona$Search.Fun, "Search More Enjoyable", "Same"))
table(sona$time.compare)

```




























































### Strategy Preference


(With sample as factor)
```{r}
chisq.test(table(sona$Choice, sona$Study))
table(sona$Choice, sona$Study)
```

```{r}
chisq.test(table(sona$Choice))
table(sona$Choice)
40/78 # number of individuals choosing organization
```





### Time, Effort, & Enjoyability Estimates Predicting Choice


```{r}
# sona.pre<-glm(Choice.Num ~ PreTimeDiff, family="binomial", data=sona)
sona.time<-glm(Choice.Num ~ PreTimeDiff, family="binomial", data=sona[sona$PreTimeDiff<70,])
sona.eff<-glm(Choice.Num ~ PreEffDiff, family="binomial", data=sona[sona$PreTimeDiff<70,])
sona.fun<-glm(Choice.Num ~ FunDiff, family="binomial", data=sona[sona$PreTimeDiff<70,])

tab_model(sona.time, sona.eff, sona.fun, transform=NULL, show.stat = T, digits.p=2)
```


Same models 2-4 as above except looking at whether they interact with sample

```{r}
sona.time2<-glm(Choice.Num ~ PreTimeDiff*Study, family="binomial", data=sona[sona$PreTimeDiff<70,])
sona.eff2<-glm(Choice.Num ~ PreEffDiff*Study, family="binomial", data=sona[sona$PreTimeDiff<70,])
sona.fun2<-glm(Choice.Num ~ FunDiff*Study, family="binomial", data=sona[sona$PreTimeDiff<70,])

tab_model(sona.time2, sona.eff2, sona.fun2, transform=NULL, show.stat = T, digits.p=2)
```

```{r}
sona.time.e2a<-glm(Choice.Num ~ PreTimeDiff, family="binomial", data=sona[sona$Study=="Sona E1" & sona$PreTimeDiff<70,])
sona.time.e2b<-glm(Choice.Num ~ PreTimeDiff, family="binomial", data=sona[sona$Study=="Sona E2" & sona$PreTimeDiff<70,])

tab_model(sona.time.e2a, sona.time.e2b, transform=NULL, show.stat = T, digits.p=2)

```





### Correlation between estimated task time, effort, & enjoyability

```{r}
corrgram(sona[c("PreTimeDiff", "PreEffDiff", "FunDiff")],
         lower.panel=panel.pts, upper.panel=panel.conf,
         diag.panel=panel.density)
```

```{r}
iv2<-sona[c("PreTimeDiff", "PreEffDiff", "FunDiff")]
names(iv2)<-c("Relative Task Time", "Relative Task Effort", "Relative Task Enjoyability")

apa.cor.table(iv2, table.number = 2, filename = "LegoOnline_Table2.doc")

```


Model with all factors combined
```{r}
sona.all<-glm(Choice.Num ~ PreTimeDiff+PreEffDiff+FunDiff, family="binomial", data=sona[sona$PreTimeDiff<70,])
sona.all2<-glm(Choice.Num ~ PreTimeDiff*Study+PreEffDiff*Study+FunDiff*Study, family="binomial", data=sona[sona$PreTimeDiff<70,])
# quasi-separation issues; removed outliers with a relative time difference score > 70

tab_model(sona.all, transform=NULL, show.stat = T, digits.p=2)
```



Standardized Coef
```{r}
sona.all3<-glm(Choice.Num ~ scale(PreTimeDiff)+scale(PreEffDiff)+scale(FunDiff), family="binomial", data=sona[sona$PreTimeDiff<70,])
mturk.all3<-glm(Choice.Num ~ scale(PreTimeDiff)+scale(PreEffDiff)+scale(FunDiff), family="binomial", data=mturk[mturk$PreTimeDiff<70,])

tab_model(mturk.all3, sona.all3, transform=NULL, show.stat = T, digits.p=2)

```







```{r}
ggplot(sona, aes(x=PreTimeDiff, y=Choice.Num)) + 
  geom_point(position = "jitter") + 
  stat_smooth(method="glm", method.args=list(family="binomial"), se=FALSE)

# par(mar = c(4, 4, 1, 1)) # Reduce some of the margins so that the plot fits better
# plot(dat$mpg, dat$vs)
# curve(predict(logr_vm, data.frame(mpg=x), type="response"), add=TRUE) 
```

```{r}
plot_model(sona.pre3, type="int")
```





































```{r load data sets: inter-rater reliability}
irr<-read.csv("C:/Users/MonaZhu/Dropbox/CANB Lab/Lego & Search/Combined Data/Lego_Combined in-Lab&Turk&Sona_InterRaterReliability.csv")
```















